Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2025-02-19 demystify.tex
updates

Moreover, do not make up stories or exaggerate your experiences.  Just show your awareness and understanding of the topic and what you did or how you plan to contribute to it (e.g., mentoring students, helping others). One of the best DEI statements I have read starts the acknowledgement that the applicant is not a minority, but a white male in a STEM field (i.e., they are the majority), and that they do not have much experience in DEI, but show that they are aware of the challenges faced by minority groups and how they can contribute to it.
\end{commentbox}

>>>>

Moreover, do not make up stories or exaggerate your experiences.  Just show your awareness and understanding of the topic and what you did or how you plan to contribute to it (e.g., mentoring students, helping others). One of the best statements I have read starts the acknowledgement that the applicant is not a minority, but a white male in a STEM field (i.e., they are the majority), and that they do not have much experience in DEI, but show that they are aware of the challenges faced by minority groups and how they can contribute to it.
\end{commentbox}
